% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{url}
\usepackage{hyperref}

\begin{document} 
 \vspace*{-0.3in}
\name{Mostafa Uddin\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Present Address} \\109 Northampton Dr. \\
Holmdel, NJ 07733}
\address{{\bf Contact} \\ mostafa.uddin@nokia.com \\ (414)379-5199 \\
       \url{http://www.cs.odu.edu/~muddin}}

 
\begin{resume} 
 

\section{Objective} Pursue a successful research career in different areas of Network System.




\section{Research Interest} 
My research interest spans in various areas of  \textbf{Mobile Computing}, \textbf{Wireless Network}, \textbf{Data Center Network}, \textbf{Software Defined Network}, and \textbf{Network Security}. I am specially interested in developing algorithms and building real-world systems that involves with Smart devices, Wireless communication, Sensing technology, Signal processing, Software Defined Networking and Applied Machine learning techniques. In developing such systems and applications, I address research challenges in the direction of energy efficiency, bandwidth improvement, ensuring E2E QoS, user's mobility, network security etc. 
  

\section{Education} 

Old Dominion University, Norfolk, VA, USA\\
PhD in Computer Science (2011 - 2016)\\
Advisor: Dr. Tamer Nadeem (nadeem@cs.odu.edu)\\
Dissertation Topic: {Toward Open and Programmable Wireless Network Edge } [Defended on May 10]\\ 
Dissertation Committee: Dr. Kurt Maly (CS, ODU), Dr. Michele Weigle (CS, ODU), Dr. ChunSheng Xinand (ECE, ODU), Prof. Mahadev Satyanarayanan (CMU)\\  
CGPA 3.98/4.0

Bangladesh University of Engineering and Technology, Dhaka, Bangladesh \\
B.S. in Computer Science and Engineering, 2006\\
CGPA 3.72/4.0

%Currently, my research focuses on developing performance and energy efficient wireless communication for smart devices. I am  exploiting multiple wireless interface like WiFi, Bluetooth, Acoustic, etc. of the Smart Phone to improve the throughput, fairness and energy efficiency of the wireless communication. Besides I am also interested in developing high accuracy indoor localization system for smartphones.

%Recently I have been collaborating with HP Labs in  "Wireless Software Define Network" project.  

\section{Industrial Experiences}

 {\bf Network System Researcher,} Bell Labs, Holmdel, NJ \hfill \textbf{June, 2016 - Present} \\

 {\bf Bell Lab Researcher - intern,} Bell Labs, Murray Hill, NJ \hfill \textbf{June, 2015 - August, 2015} \\
 Advisor: \textbf{Randeem Bhatia} 
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Evaluating different techniques of network flow sampling in Open vSwitch(e.g. sFlow, NetFlow, mirroring) based on CPU utilization and bandwidth reductions.
 \item Developing adaptive and efficient flow sampling actions in the OVS Datapath.
 \item Developing algorithm for detecting any network anomalies or attacks using the sampled network flow statistics.
 \end{itemize}

{\bf Research Associate Intern,} HP Labs, Palo Alto, CA \hfill \textbf{July,2014 - August,2014} \\
Mentor: \textbf{Kyu-Han KIM}, Senior Researcher and Research Manager
\begin{itemize} \itemsep -2pt %reduce space between items
\item Leveraging both the cellular (i.e. LTE) and the WiFi interface of the smartphone for improving the performance of the peer-to-peer real-time interactive applications such as Skype video chat, Google Hangout, Viber voice call etc.
\item Hack the network stack of the Nexus 7 tablet (LTE) to implement the Multi-Path UDP(MPUDP) in the transportation layer of the android kernel.
\item Experimental evaluation of our system using 2 Nexus 7 tablet (android device) using AT\&T vendors
\end{itemize}

{\bf Research Associate Intern,} HP Labs, Palo Alto, CA \hfill \textbf{May,2013 - August,2013} \\
Mentor: \textbf{Jeongkeun Lee}, Senior Research Scientist
\begin{itemize} \itemsep -2pt %reduce space between items
\item Extending the SDN framework to the wireless end devices.
\item WLAN virtualization with performance guarantee.
\item Implementing customized Qdisc for Linux Network stack.
\item Implementing required interaction between WiFi driver and Linux Qdisc. 
\item Deploying open vSwitch in Android platform using cross-platform compiling.
\end{itemize}

{\bf Software Engineer,} KAZ (www.kaz.com.bd), Dhaka, Bangladesh \hfill \textbf{Feb '08-Dec '09}
\begin{itemize} \itemsep -2pt
\item Research and Development in ITE Enterprise project, an international tax management tool. 
\item Developing an installer and auto updating mechanism using InstallShield 2008 for the ITE Enterprise product.
\item Programming in C\#, WCF and WPF.
\end{itemize}

{\bf Software Engineer,} SDSL(www.sdslbd.com), Dhaka, Bangladesh \hfill \textbf{Nov '06-Feb '08}
\begin{itemize} \itemsep -2pt
\item  GPS based Real-Time Navigation system for Mobile devices using Symbian C++/S60. 
\item  Instant Mobile Messenger Application for Mobile devices in Symbian OS.
\item  Developing Mobile Map(http://maps.afrigis.co.za/mobi/splash.html), a J2ME mobile application.
\item  Developing GRID(http://www.thegrid.co.za/about), a J2ME mobile application.
\end{itemize}

{\bf Software Engineer Intern} Vertex Limited, Dhaka, Bangladesh \hfill \textbf{Dec '05 - May '06}
\begin{itemize} \itemsep -2pt
\item  Developing software for the RTA-600 Time attendance device. (Java)
\end{itemize}


\section{Academic Experiences}

 {\bf Research Assistant,} Computer Science, ODU, Norfolk, VA \hfill \textbf{Fall  2011-present} \\
 Advisor: \textbf{Dr. Tamer Nadeem}, Assistant Professor
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item \textbf{TrafficVision:} In this project, we design and develop modules that extend the SDN's layer architecture to have fine-grained and real-time traffic-awareness at the network edge. We extend the SDN's data layer and Southbound-API to extract new traffic flow feature, that allow us to develop tool (e.g. \textit{TrafficVision}) in the control layer to have scalable,economic and flexible solutions of classifying the network traffic flows based on novel Machine-Learning (ML) technique. This is a collaboration research project with HP Labs, Palo Alto, CA. 
 \item \textbf{CHKD}: In this project, we use accelerometer, gyroscope, and compass sensors of the smartphone to build an automatic tool to create spaghetti diagrams of movements of personnel in a non-intrusive way.
 \item \textbf{meSDN}: In this project, we extend the SDN framework to the client devices to provide services such as WLAN virtualization with end-to-end QoS. This is a collaboration research project with HP Labs, Palo Alto, CA.
 \item \textbf{Audio-WiFi}:  In this project, we build a novel framework that integrate the Audio interface (mic,speaker, and sound driver) with the Wi-Fi Interface to develop a more efficient Wi-Fi network communication for smart devices.
 \item \textbf{MagnoTricorder}: In this project, we leverage the effect of Electro Magnetic Interference (EMI) generated by the AC current in the main power-line at home to identifying and detecting the running devices. In this project we use magnetic field sensor of the smartphone, signal processing, and machine learning technique to build the system.
 \item \textbf{EnergySniffer}: In this project we use the acoustic sensors of the smartphone to identify the running machines at home. We use signal processing and machine learning technique to build such system. 
 \item \textbf{ParkZoom}: This is an infrastructure aided smartphone sensing based parking localization system. This is a collaboration project with Siemens Corporate Research to develop smart parking system. 
 \end{itemize}

{\bf Teaching Assistant,} Computer Science, ODU, Norfolk, VA \hfill \textbf{Fall  2011-present}
\begin{itemize} \itemsep -2pt %reduce space between items
\item  CS300 - Computer in Society, Fall 2011. 
\item  CS250 - Programming and Problem Solving II, Spring 2012.
\item CS495/595 - App Development for Smart Devices, Fall 2012.
\item CS495/595 - App Development for Smart Devices, Fall 2013.
\end{itemize}



 


\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    Programming Skill: & C/C++, Java, Python, C\#, SQL, JavaScript/CSS/D3, nesC \\
     Technical Skill &  Android Programming,
     					     Linux Kernel Programming, 
					     Open vSwitch (user-space and kernel space)					
					     Linux Network Stack (IP, Qdisc, Bridge, Core, mac80211 etc.) hacking,
					     Wireless Driver Hacking(Qualcomm, Broadcom, TI etc.)
					     Audio Driver Hacking (ALSA), Signal Processing, Machine learning, Smartphone Power Monitoring(Monsoon), 
					     USRP and GNU Radio, MATLAB, Octave, Weka-Data mining tool, TinyOS- TelosB Sensor.
 \end{tabular}



\section{Papers:} 
\begin{itemize} \itemsep -2pt
                % \item Beacon-Beep: Light-Weight High-Accuracy Localization System for Smartphones (under review) \\ Mostafa Uddin and Tamer Nadeem\\
                  %Submitted in: ACM MobiSys 2013 



\item SafeEnd: An Application-Aware Programmable Network Security Solution for Mobile Devices (In preparation)\\
Mostafa Uddin, and Tamer Nadeem 

\item SmartEdge: Toward Making Wireless Network Edges Traffic-Aware (in preparation)\\
Mostafa Uddin, Ibrahim Ben Mustafa, and Tamer Nadeem

\item TrafficVision: A Case Scenario of Pushing SDN to Wireless Edges (in review)\\
Mostafa Uddin, Gowtham Bellala, Jeongkeun Lee, and Tamer Nadeem

\item Understanding the Intermittent Traffic Pattern of HTTP Video Streaming over Wireless Networks\\
Ibrahim Ben Mustafa, Mostafa Uddin, and Tamer Nadeem\\
WINMEE 2016

\item Wearable Sensing Framework for Human Activity Monitoring \\
Mostafa Uddin, Ahmed Salem, Ilho Nam, and Tamer Nadeem \\
ACM WearSys'15
                 
\item Harmony: Content Resolution using Acoustic Channel (acceptance rate 19\% = 316/1640) [To appear]\\
Mostafa Uddin, and Tamer Nadeem \\
IEEE INFOCOM 2015

\item meSDN: mobile extension of SDN \\
Jeongkeun Lee, Mostafa Uddin, JeanTourrilhes, Souvik Sen, Sujata Banerjee, Manfred Arndt, Kyu-Han Kim, Tamer Nadeem\\ 
ACM MCS 2014 (with MobiSys 2014). 

\item SpyLoc: A Light Weight Localization System for Smartphones.(acceptance rate 19.8\% = 68/342)\\
Mostafa Uddin and Tamer Nadeem\\ 
IEEE SECON 2014. 

\item SmartSpaghetti: Accurate and Robust Tracking of Human's Location\\
Mostafa Uddin, Ajay Gupta, Kurt Maly, Tamer Nadeem, Sandip Godambe, Arno Zaritsky\\ 
IEEE-EMBS International Conferences on Biomedical and Health Informatics, 2014 

\item SmartSpaghetti: Use of Smart Devices to Solve Health Care Problems (Full Paper acceptance rate=18\%)\\
Mostafa Uddin, Ajay Gupta, Kurt Maly, Tamer Nadeem, Sandip Godambe, and Arno Zaritsky\\ 
International Workshop on Biomedical and Health Informatics, BIBM 2013 

\item RF-Beep: A light ranging scheme for smart devices (acceptance rate 11.2\% = 19/170(full paper))\\
Mostafa Uddin and Tamer Nadeem\\ 
IEEE PerCom 2013. 

\item A2PSM: Audio Assisted Wi-Fi Power Saving Mechanism for Smart Devices(acceptance rate 31.5\%)\\ 
Mostafa Uddin and Tamer Nadeem\\ 
ACM HotMobile 2013. 

\item MagnoTricorder: What You Need To Do Before Leaving Home\\ 
Mostafa Uddin and Tamer Nadeem\\ 
ACM HomeSys, UbiComp 2012 

\item EnergySniffer: Home Energy Monitoring System using Smart Phones [Slide]\\ 
Mostafa Uddin and Tamer Nadeem\\ 
IEEE IWCMC, 2012. 

 \end{itemize}
           
\section{Articles:}
\begin{itemize} \itemsep -2pt

\item Report of HotMobile 2012\\
Igor Pernek, Mostafa Uddin and Jack Fernando Bravo Torres\\ 
IEEE Pervasive Computing. 

\item HotMobile 2012 Poster: MachineSense: Detecting and Monitoring Active Machines using Smart Phone\\ 
Mostafa Uddin and Tamer Nadeem\\ 
ACM SIGMOBILE MC2R. 

\item HotMobile 2012 Poster: Audio-WiFi: Audio Channel Assisted WiFi Network for Smart Phones\\ 
Mostafa Uddin and Tamer Nadeem\\ 
ACM SIGMOBILE MC2R. 

 \end{itemize}
 
\section{Demos/Posters:}
\begin{itemize} \itemsep -2pt

\item Poster: Extending SDN for mobile device \\Jeongkeun Lee,  Mostafa Uddin, Jean Tourrilhes, Souvik Sen, Sujata Banerjee,
Manfred Arndt and Tamer Nadeem \\
		ACM HotMobile 2014

\item SpyLoc: a Light Weight Localization System for Smartphones [Poster][SRC Presentation]\\
Mostafa Uddin and Tamer Nadeem\\ 
In Proceedings of MobiCom'13 

\item Audio-WiFi: Audio Channel Assisted WiFi Network for Smart Phones[Demo]\\ 
Mostafa Uddin and Tamer Nadeem\\ 
IEEE INFOCOM, 2012 . 

\item EnergySniffer: Home Energy Monitoring System using Smart Phones[Poster]\\ 
Mostafa Uddin and Tamer Nadeem\\ 
IEEE INFOCOM, 2012 . 

\item MachineSense: Detecting and Monitoring Active Machines using Smart Phones[Poster]\\ 
Mostafa Uddin and Tamer Nadeem\\ 
ACM HotMobile, 2012 . 

\end{itemize}
 
 

\section{Patents and Invention Disclosures}
Jung Gun Lee, Mostafa Abdulla Zahid Uddin, Jean Tourrilhes, Souvik Sen, Manfred R Arndt. "Wireless Software-Defined Networking", Publication number WO2015065422 A1, Publication date May 7, 2015. \\
\\
Mostafa Uddin, Tamer Nadeem. "SMILE -- Towards Smarter Network Edges for Next Generation Networks", Filling Date Oct, 2015.\\

\section{DBLP \& Google Scholar}
\href{http://dblp.uni-trier.de/pers/hd/u/Uddin:Mostafa}{DBLP Profile} \\
\href{https://scholar.google.com/citations?user=6uSlsIIAAAAJ&hl=en}{Google Scholar Profile}\\


\section{News/Media}
\href{http://www.v3.co.uk/v3-uk/the-frontline-blog/2240952/researchers-develop-sound-way-to-improve-smartphone-battery-life}{Researchers develop sound way to improve smartphone battery life(V3 online Magazine)}

\section{Awards}
ACM SIGMOBILE Travel grant for attending HotMobile 2015. \\
ACM SIGMOBILE Travel grant for attending HotMobile 2014. \\
Microsoft Research "ACM SRC" Grant Recipient for MobiCom 2013, Miami, FL. \\
NSF Student Travel Grant Recipient for MobiCom 2013, Miami, FL. \\
NSF Travel grant for attending IEEE PerCom 2013. \\
ACM SIGMOBILE Travel grant for attending HotMobile 2013. \\
Outstanding RA (fall 2012) - Computer Science Department. \\
Travel grant for attending HoMobile 2012, INFOCOM 2012, and Ubicomp2012(from CS Department of  ODU).\\
Dominion Graduate Scholar offered by College of Sciences ODU.\\ 
Dean's List Scholarship during undergraduate studies at BUET. \\
Placed in top 1\% in Higher Secondary Exam (A-level) in Bangladesh. \\
Placed in top 1\% in Secondary School Exam (O-level) in Bangladesh. \\ 


\section{Professional Services}
Student Volunteer in MobiCom'2013, HotMobile'2013, HotMobile'2014, DriveSense'2014 \\
Invited Reviewer IEEE Internet of Things Journal (IoT), ACM/IEEE Transactions on Networking (ToN) \\
Reviewer through Advisor: IEEE INFOCOM 2016, IEEE LCN 2015, ACM HotMobile 2015, IEEE SECON 2015, IEEE ICC 2014, IEEE PerCom'2014, IEEE Globecom' 2013, IEEE IWCMC'2013.\\

 

\section{Membership \& Activities}
ACM SIGMOBILE Student Member\\
ACM Student Member \\
ODU Bangladeshi Student Association, President\\
%Member of Software Design Group ( http://sdgbuet.tripod.com ),\\
%Bangladesh University of Engineering \& Technology(Feb 2003- Nov 2006).\\

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide

\end{resume} 
\end{document} 



